---
title: "GDP_FireFloodWind_DID_Danielle"
output: html_document
date: "2025-02-05"
---

```{r setup, include=FALSE}

#library(sf)
#library(terra)
library(dplyr)
library(readr)
library(data.table)
library(ggplot2)
library(purrr)
library(parallel)
options(scipen = 999)

if(!require(pacman)){install.packages("pacman"); library(pacman)}
p_load(dplyr, lfe, coefplot, data.table, sandwich, lmtest, stringr, MatchIt, DiDforBigData, fixest, tidyverse, broom, ggthemes)

num_cores<- detectCores()-5

`%!in%` = Negate(`%in%`)


```


# GDP 


```{r}
#gdp 
final_gdp_df <- readRDS(file = "/mnt/theia/implications/dmed_global_data/Global Implications Datasets/global_dat_ready.rds")

final_gdp_df<- final_gdp_df %>% mutate(INCOME_URBAN=paste0(INCOME_GRP, ", ", urban))

final_gdp_df<- final_gdp_df %>% select(tile_id, ISO_A3, NAME, 
                                       ECONOMY, urban, ECON_URBAN,
                                       INCOME_URBAN, INCOME_GRP,
                                       GDP2000:GDP2020, POP_CHANGE)

final_gdp_df<- final_gdp_df %>% mutate(POP_LOSS=ifelse(POP_CHANGE<0, "T", "F")) %>% 
  mutate(ECON_POPLOSS=paste0(ECONOMY, ", ", POP_LOSS))

final_gdp_df <- final_gdp_df %>%
  pivot_longer(cols = starts_with("GDP"),  # Select all columns starting with "GDP"
               names_to = "year",        # New column for years
               values_to = "gdp_value")      # New column for values

final_gdp_df <- final_gdp_df %>%
  mutate(year = as.numeric(gsub("GDP", "", year)))



#drop areas where GDP was ever zero
final_gdp_df <- final_gdp_df %>%
  group_by(tile_id) %>%
  filter(all(!is.na(gdp_value))) %>%  # Keep only rows where gdp_value is not NA for the entire group
  ungroup()

```


# FIRE


### Read and prep data 

```{r}

#fire
global_fire_all_years <- read.csv('/mnt/theia/implications/global_fire_exposure_v2/global_fire_all_first_4_or_less.csv')

look<- global_fire_all_years %>% group_by(year) %>% summarise(sum(years_since_first_hit==1, na.rm = T))

#fire data not available until 2004 
global_fire_all_years<- global_fire_all_years %>% filter(year>=2004)

# Merge datasets and clean them
global_fire_full <- inner_join(global_fire_all_years, 
                              final_gdp_df, by=c("tile_id","year"))



summary(global_fire_full$year)

length(unique(global_fire_full$tile_id))

count_obs<- global_fire_full %>% 
  group_by(ECON_URBAN) %>% summarise(n_areas=length(unique(tile_id)), n_fires=sum(first_fire_event==1, na.rm = T))


global_fire_full %>% group_by(tile_id) %>% summarise(fire_count=sum(first_fire_event==1, na.rm = T)) %>% ungroup() %>% 
  group_by(fire_count) %>% summarise(n())



# Make Event-Time Variables and Adjust for Inflation Sale Prices
global_fire_full <- global_fire_full %>%
  mutate(minus_seven = ifelse(years_since_first_hit <= -7 & !is.na(years_since_first_hit), 1, 0),
         minus_six = ifelse(years_since_first_hit == -6 & !is.na(years_since_first_hit), 1, 0),
         minus_five = ifelse(years_since_first_hit == -5 & !is.na(years_since_first_hit), 1, 0),
         minus_four = ifelse(years_since_first_hit == -4 & !is.na(years_since_first_hit), 1, 0),
         minus_three = ifelse(years_since_first_hit == -3 & !is.na(years_since_first_hit), 1, 0),
         minus_two = ifelse(years_since_first_hit == -2 & !is.na(years_since_first_hit), 1, 0),
         minus_one = ifelse(years_since_first_hit == -1 & !is.na(years_since_first_hit), 1, 0),
         plus_zero = ifelse(years_since_first_hit == 0 & !is.na(years_since_first_hit), 1, 0),
         plus_one = ifelse(years_since_first_hit == 1 & !is.na(years_since_first_hit), 1, 0),
         plus_two = ifelse(years_since_first_hit == 2 & !is.na(years_since_first_hit), 1, 0),
         plus_three = ifelse(years_since_first_hit == 3 & !is.na(years_since_first_hit), 1, 0),
         plus_four = ifelse(years_since_first_hit == 4 & !is.na(years_since_first_hit), 1, 0),
         plus_five = ifelse(years_since_first_hit == 5 & !is.na(years_since_first_hit), 1, 0),
         plus_six = ifelse(years_since_first_hit == 6 & !is.na(years_since_first_hit), 1, 0),
         plus_seven = ifelse(years_since_first_hit == 7 & !is.na(years_since_first_hit), 1, 0),
         plus_eight = ifelse(years_since_first_hit == 8 & !is.na(years_since_first_hit), 1, 0),
         plus_nine = ifelse(years_since_first_hit == 9 & !is.na(years_since_first_hit), 1, 0),
         plus_ten = ifelse(years_since_first_hit == 10 & !is.na(years_since_first_hit), 1, 0),
         plus_eleven = ifelse(years_since_first_hit == 11 & !is.na(years_since_first_hit), 1, 0),
         plus_twelve = ifelse(years_since_first_hit == 12 & !is.na(years_since_first_hit), 1, 0))




```




```{r}

#fyi list of countries by economy 


Countries_by_Econ<- global_fire_full %>% 
  group_by(ECONOMY) %>% 
  summarise(Countries = paste(unique(NAME), collapse = ", "))

write_csv(Countries_by_Econ, "/home/dmedgyesi/international/DID/results/Countries_by_Econ_List.csv")


Count_pop_loss<- global_fire_full %>% 
  group_by(POP_LOSS) %>% 
  summarise(n_distinct(tile_id))

```

### DID all data combined  

prep

```{r}

# cohort: year that exposure happened
global_fire_full <- global_fire_full %>% 
  mutate(cohort = ifelse(years_since_first_hit == 0, year, NA))  %>%
  group_by(tile_id) %>%
  arrange(tile_id, year) %>%
  fill(cohort) %>%
  group_by(tile_id) %>%
  arrange(tile_id, -year) %>%
  fill(cohort) %>%
  arrange(tile_id, year) %>%
  mutate(cohort = ifelse(is.na(cohort),Inf,cohort))

full <- global_fire_full %>% select(tile_id, ECONOMY, urban, ECON_URBAN, 
                                    INCOME_URBAN, INCOME_GRP,
                                    POP_LOSS, POP_CHANGE, ECON_POPLOSS,gdp_value, year, cohort) %>%
  setDT()


full<- full %>% mutate(gdp_value_log=log(gdp_value))



# Filter out cohorts that don't have sufficient pre-period data
valid_cohorts <- full %>%
  group_by(tile_id) %>%
  mutate(has_preperiod = any(year == cohort - 1)) %>%
  filter(has_preperiod) %>%
  pull(cohort) %>%
  unique()

full_filtered <- full %>%
  filter(cohort %in% valid_cohorts)




```

model

```{r}



#specify variables
varnames = list()
varnames$time_name = "year" 
varnames$outcome_name = "gdp_value_log"
varnames$cohort_name = "cohort"
varnames$id_name = "tile_id"

#varnames$covariate_names = "month" 


did = DiD(inputdata = full_filtered, 
          varnames = varnames,
          base_event = -1,
          min_event = -5, 
          max_event = 10, parallel_cores = num_cores, control_group = "future-treated")

print(did$results_average)

coef_did_combined <- tibble(did$results_average)



coef_did_combined<-coef_did_combined %>% mutate(ATT_perc=100*(exp(ATTe)-1), 
                         lower_perc=100*(exp(ATTe - 1.965 * ATTe_SE)-1),
                         upper_perc=100*(exp(ATTe + 1.965 * ATTe_SE)-1))


write_csv(coef_did_combined, "/home/dmedgyesi/international/DID/results/tables/Fire_GDP_AllData_DID_tables.csv")


```

plot

```{r}



ggplot(coef_did_combined, aes(x = EventTime, y = ATT_perc)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Fire Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) 


ggsave("/home/dmedgyesi/international/DID/results/DID_Fire_GDP_AllData.png", width = 11, height = 8, dpi = 300)




```


### DID by Economy

model 

```{r}


varnames = list()
varnames$time_name = "year" 
varnames$outcome_name = "gdp_value_log"
varnames$cohort_name = "cohort"
varnames$id_name = "tile_id"

# Store results in a list
did_results <- list()
did_results_cohort<- list()

# Get unique economy classes
economy_classes <- unique(full_filtered$ECONOMY)

# Loop through economy classes
for (econ in economy_classes) {
  
  # Filter dataset for the current economy class
  filtered_data <- full_filtered %>%
    filter(ECONOMY == econ)
  
  # Run DiD model
  did <- DiD(inputdata = filtered_data, 
             varnames = varnames, 
             base_event = -1,
             min_event = -5, 
             max_event = 10, parallel_cores = num_cores, control_group = "future-treated")
  
  # Store results with economy class label
  did_results[[econ]] <- tibble(economy = econ, did$results_average)
  did_results_cohort[[econ]]<- tibble(economy=econ, did$results_cohort)
}

# Combine all results into one dataframe
coef_did_econ <- bind_rows(did_results)
coef_did_cohort_econ <- bind_rows(did_results_cohort)


coef_did_econ<-coef_did_econ %>% mutate(ATT_perc=100*(exp(ATTe)-1), 
                         lower_perc=100*(exp(ATTe - 1.965 * ATTe_SE)-1),
                         upper_perc=100*(exp(ATTe + 1.965 * ATTe_SE)-1))


coef_did_cohort_econ<-coef_did_cohort_econ %>% mutate(ATT_perc=100*(exp(ATTge)-1), 
                         lower_perc=100*(exp(ATTge - 1.965 * ATTge_SE)-1),
                         upper_perc=100*(exp(ATTge + 1.965 * ATTge_SE)-1))


write_csv(coef_did_econ, "/home/dmedgyesi/international/DID/results/tables/Fire_GDP_Econ_DID_tables.csv")


```

plot

```{r}

ggplot(coef_did_econ, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Fire Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Fire_GDP_Econ.png", width = 11, height = 8, dpi = 300)





#Developed
coef_did_econ_developed<- coef_did_econ %>% filter(substr(economy,1,1) %in% c(1,2))

ggplot(coef_did_econ_developed, aes(x = EventTime, y =ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Fire Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Fire_GDP_Econ_Developed.png", width = 11, height = 8, dpi = 300)



#Emerging
coef_did_econ_emerge<- coef_did_econ %>% filter(substr(economy,1,1) %in% c(3,4,5))

ggplot(coef_did_econ_emerge, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin =lower_perc, 
                      ymax =upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Fire Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Fire_GDP_Econ_Emerge.png", width = 11, height = 8, dpi = 300)



#Developing
coef_did_econ_not_develop<- coef_did_econ %>% filter(substr(economy,1,1) %in% c(6,7))

ggplot(coef_did_econ_not_develop, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Fire Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Fire_GDP_Econ_NotDevelop.png", width = 11, height = 8, dpi = 300)




```



select results

```{r}

fire_results_econ<- coef_did_econ %>% filter(EventTime>=0) %>% mutate(YearsCAT=cut2(EventTime, cuts = c(0,4,7,10)))

fire_results_econ<- fire_results_econ %>% group_by(economy, YearsCAT) %>% mutate(flg=case_when(ATT_perc==min(ATT_perc)~T, TRUE~F)) %>% ungroup() %>% filter(flg==T)

vars<- c("ATTe", "ATTe_SE", "ATT_perc", "lower_perc", "upper_perc")

fire_results_econ <- fire_results_econ %>%
  mutate(across(all_of(vars), ~ ifelse(ATT_perc > 0, 0, .)))




ggplot(fire_results_econ, aes(x = YearsCAT, y = ATT_perc, color=economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the severe fire event occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class


ggsave("/home/dmedgyesi/international/DID/results/DID_Fire_GDP_Econ_FINAL.png", width = 11, height = 8, dpi = 300)





```


plot by cohort

```{r}

coef_did_cohort_econ<- coef_did_cohort_econ %>% 
  mutate(period=case_when(Cohort %in% 2003:2009~"2003-2009", 
                          Cohort %in% 2010:2016~"2010-2016", 
                          TRUE~"2017-2021"))

# Get unique economy classes
economy_classes <- unique(coef_did_cohort_econ$economy)

# Loop through each economy class
for (econ in economy_classes) {
  
  # Filter data for the current economy class
  df_filtered <- coef_did_cohort_econ %>% filter(economy == econ)
  
  # Create plot
  p <- ggplot(df_filtered, aes(x = EventTime, y = ATT_perc,shape=period, 
                               color =period)) +
    geom_pointrange(aes(ymin = lower_perc, ymax = upper_perc), linewidth = 0.25) +
    geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
    geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
    xlab("Years since the First Fire Event Occurred") +
    ylab("GDP Percentage Change, 95% C.I.") +
    theme_bw() +
    theme(plot.background = element_rect(fill = "white"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          axis.line.y = element_line(color = "black"),
          axis.line.x = element_line(color = "black")) +
    ggtitle(paste("GDP Impact -", econ))  # Add title for clarity

  # Define the file name dynamically
  file_name <- paste0("/home/dmedgyesi/international/DID/results/plot_cohort/DID_Fire_GDP_Econ_", econ, ".png")
  
  # Save the plot
  ggsave(file_name, plot = p, width = 6, height = 6, dpi = 300)
  
  print(p)
  }


```



### DID by Economy and Urbanicity 

model

```{r}



varnames = list()
varnames$time_name = "year" 
varnames$outcome_name = "gdp_value_log"
varnames$cohort_name = "cohort"
varnames$id_name = "tile_id"



# Store results in a list
did_results <- list()

# Get unique economy classes
economy_classes <- unique(full_filtered$ECON_URBAN)

# Loop through economy classes
for (econ in economy_classes) {
  
  # Filter dataset for the current economy class
  filtered_data <- full_filtered %>%
    filter(ECON_URBAN == econ)
  
  # Run DiD model
  did <- DiD(inputdata = filtered_data, 
             varnames = varnames, 
             base_event = -1,
             min_event = -5, 
             max_event = 10, parallel_cores = num_cores, control_group = "future-treated")
  
  # Store results with economy class label
  did_results[[econ]] <- tibble(economy = econ, did$results_average)
}

# Combine all results into one dataframe
coef_did_econurban <- bind_rows(did_results)


coef_did_econurban<-coef_did_econurban %>% mutate(ATT_perc=100*(exp(ATTe)-1), 
                         lower_perc=100*(exp(ATTe - 1.965 * ATTe_SE)-1),
                         upper_perc=100*(exp(ATTe + 1.965 * ATTe_SE)-1))



write_csv(coef_did_econurban, "/home/dmedgyesi/international/DID/results/tables/Fire_GDP_EconUrban_DID_tables.csv")



```

plot

```{r}

coef_did_econurban<- coef_did_econurban %>% 
  mutate(urban=str_sub(economy, start= -1), 
                              economy_only=str_sub(economy, start=1,end= -4)) %>% 
  mutate(economy_label=paste0(economy_only, ", ", ifelse(urban=="F", "Rural", "Urban"))) %>% 
  select(economy, economy_only, urban,economy_label, everything())


ggplot(coef_did_econurban, aes(x = EventTime, y = ATT_perc, color = economy_only, shape = urban)) +
  geom_pointrange(aes(ymin =lower_perc, 
                      ymax =upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Fire Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black"), 
        legend.position = "none") +
facet_wrap(~ economy_label, ncol=4) 

ggsave("/home/dmedgyesi/international/DID/results/DID_Fire_GDP_EconUrban.png", width = 11, height = 8, dpi = 300)


#Developed
coef_did_econurban_developed<- coef_did_econurban %>% filter(substr(economy,1,1) %in% c(1,2))

ggplot(coef_did_econurban_developed, aes(x = EventTime, y =ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Fire Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Fire_GDP_EconUrban_Developed.png", width = 11, height = 8, dpi = 300)



#Emerging
coef_did_econurban_emerge<- coef_did_econurban %>% filter(substr(economy,1,1) %in% c(3,4,5))

ggplot(coef_did_econurban_emerge, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin =lower_perc, 
                      ymax =upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Fire Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Fire_GDP_EconUrban_Emerge.png", width = 11, height = 8, dpi = 300)



#Developing
coef_did_econurban_not_develop<- coef_did_econurban %>% filter(substr(economy,1,1) %in% c(6,7))

ggplot(coef_did_econurban_not_develop, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Fire Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Fire_GDP_EconUrban_NotDevelop.png", width = 11, height = 8, dpi = 300)






```

select results

```{r}

fire_results<- coef_did_econurban %>% filter(EventTime>=0) %>% mutate(YearsCAT=cut2(EventTime, cuts = c(0,4,7,10)))

fire_results<- fire_results %>% group_by(economy, YearsCAT) %>% mutate(flg=case_when(ATT_perc==min(ATT_perc)~T, TRUE~F)) %>% ungroup() %>% filter(flg==T)

vars<- c("ATTe", "ATTe_SE", "ATT_perc", "lower_perc", "upper_perc")

fire_results <- fire_results %>%
  mutate(across(all_of(vars), ~ ifelse(ATT_perc > 0, 0, .)))

fire_results<- fire_results %>% 
  mutate(type=case_when(urban=="T"~"urban", urban=="F"~"rural", TRUE~NA)) %>% 
  mutate(type=factor(type, levels = c("rural", "urban")))


ggplot(fire_results, aes(x = YearsCAT, y = ATT_perc, color = type, shape = type)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25,  position = position_dodge(width = 0.3)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the severe fire event occurred") +
  ylab("GDP Change (%), 95% CI") +
  theme_bw() +
  scale_x_discrete(labels=c("[ 0, 4)"="0-3", "[ 4, 7)"= "4-6", "[ 7,10]"="7-10"))+
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black"), 
        legend.title = element_blank()) +
  facet_wrap(~ economy_only) + # Facet by economy class
 ggtitle("Severe Fire Event — GDP Change")

ggsave("/home/dmedgyesi/international/DID/results/DID_Fire_GDP_EconUrban_FINAL.png", width = 11, height = 8, dpi = 300)





```

For journal

```{r}


fire_results<- fire_results %>% 
  mutate(type=factor(type, levels = c("urban", "rural")))

ggplot(fire_results, aes(x = YearsCAT, y = ATT_perc, fill = type)) +
  geom_col(position = position_dodge(width = 0.6), width = 0.5) +
  geom_errorbar(aes(ymin = lower_perc, ymax = upper_perc),
                position = position_dodge(width = 0.6),
                width = 0.2, linewidth = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the severe fire event occurred") +
  ylab("Max GDP Decline (%), 95% CI") +
  scale_x_discrete(labels = c("[ 0, 4)" = "0-3", "[ 4, 7)" = "4-6", "[ 7,10]" = "7-10")) +
  scale_fill_manual(values = c("rural" = "#F8766D", "urban" = "#00BFC4")) + 
  theme_bw() +
  theme(
    plot.background = element_rect(fill = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    axis.line.y = element_line(color = "black"),
    axis.line.x = element_line(color = "black"),
    legend.title = element_blank()
  ) +
  facet_wrap(~ economy_only) +
  ggtitle("Severe Fire Event — GDP Change")


ggsave("/home/dmedgyesi/international/DID/results/Fig5.png", width = 7, height = 5, dpi = 300)


ggsave("/home/dmedgyesi/international/DID/results/Fig5.eps", width = 7, height = 5)



fire_results_format<- fire_results %>% 
  mutate(`Percent Decrease (95% CI)`= paste0(sprintf("%.2f", ATT_perc), " (", 
                                             sprintf("%.2f", lower_perc), ", ", 
                                             sprintf("%.2f", upper_perc), ")")) %>% 
  select(economy_only, YearsCAT, type, `Percent Decrease (95% CI)`) %>% pivot_wider(
    names_from = type,
    values_from = `Percent Decrease (95% CI)`
  ) %>% arrange(economy_only)

write_csv(fire_results_format, "/home/dmedgyesi/international/DID/results/tables/Fire_GDP_EconUrban_DID_tables_3periods.csv")


```

### DID by Economy and Pop loss 

model

```{r}



varnames = list()
varnames$time_name = "year" 
varnames$outcome_name = "gdp_value_log"
varnames$cohort_name = "cohort"
varnames$id_name = "tile_id"



# Store results in a list
did_results <- list()

# Get unique economy classes
economy_classes <- unique(full_filtered$ECON_POPLOSS)

# Loop through economy classes
for (econ in economy_classes) {
  
  # Filter dataset for the current economy class
  filtered_data <- full_filtered %>%
    filter(ECON_POPLOSS == econ)
  
  # Run DiD model
  did <- DiD(inputdata = filtered_data, 
             varnames = varnames, 
             base_event = -1,
             min_event = -5, 
             max_event = 10, parallel_cores = num_cores, control_group = "future-treated")
  
  # Store results with economy class label
  did_results[[econ]] <- tibble(economy = econ, did$results_average)
}

# Combine all results into one dataframe
coef_did_econpop <- bind_rows(did_results)


coef_did_econpop<-coef_did_econpop %>% mutate(ATT_perc=100*(exp(ATTe)-1), 
                         lower_perc=100*(exp(ATTe - 1.965 * ATTe_SE)-1),
                         upper_perc=100*(exp(ATTe + 1.965 * ATTe_SE)-1))



write_csv(coef_did_econpop, "/home/dmedgyesi/international/DID/results/tables/Fire_GDP_EconPopLoss_DID_tables.csv")



```

plot

```{r}


coef_did_econpop<- coef_did_econpop %>% 
  mutate(pop_loss=str_sub(economy, start= -1), 
                              economy_only=str_sub(economy, start=1,end= -4)) %>% 
  select(economy, economy_only, pop_loss, everything())

ggplot(coef_did_econpop, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin =lower_perc, 
                      ymax =upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Fire Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Fire_GDP_EconPop.png", width = 11, height = 8, dpi = 300)


#Developed
coef_did_econpop_developed<- coef_did_econpop %>% filter(substr(economy,1,1) %in% c(1,2))

ggplot(coef_did_econpop_developed, aes(x = EventTime, y =ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Fire Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Fire_GDP_EconPop_Developed.png", width = 11, height = 8, dpi = 300)



#Emerging
coef_did_econpop_emerge<- coef_did_econpop %>% filter(substr(economy,1,1) %in% c(3,4,5))

ggplot(coef_did_econpop_emerge, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin =lower_perc, 
                      ymax =upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Fire Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Fire_GDP_EconPop_Emerge.png", width = 11, height = 8, dpi = 300)



#Developing
coef_did_econpop_not_develop<- coef_did_econpop %>% filter(substr(economy,1,1) %in% c(6,7))

ggplot(coef_did_econpop_not_develop, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Fire Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Fire_GDP_EconPop_NotDevelop.png", width = 11, height = 8, dpi = 300)






```

# FLOOD



### Read and prep data 

```{r}

#fire
global_flood_all_years <- read.csv('/mnt/theia/implications/global_flood_exposure_100rp_v2/global_flood_all_first_100rp.csv')


look<- global_flood_all_years %>% 
  group_by(year) %>% 
  summarise(sum(first_flood_event==1, na.rm=T))

# Merge datasets and clean them
global_flood_full <- inner_join(global_flood_all_years, 
                              final_gdp_df, by=c("tile_id","year"))



length(unique(global_flood_full$tile_id))

count_obs_flood<- global_flood_full %>% 
  group_by(ECON_URBAN) %>% summarise(n_areas=length(unique(tile_id)), n_flood=sum(first_flood_event==1, na.rm = T))



# Make Event-Time Variables and Adjust for Inflation Sale Prices
global_flood_full <- global_flood_full %>%
  mutate(minus_seven = ifelse(years_since_first_hit <= -7 & !is.na(years_since_first_hit), 1, 0),
         minus_six = ifelse(years_since_first_hit == -6 & !is.na(years_since_first_hit), 1, 0),
         minus_five = ifelse(years_since_first_hit == -5 & !is.na(years_since_first_hit), 1, 0),
         minus_four = ifelse(years_since_first_hit == -4 & !is.na(years_since_first_hit), 1, 0),
         minus_three = ifelse(years_since_first_hit == -3 & !is.na(years_since_first_hit), 1, 0),
         minus_two = ifelse(years_since_first_hit == -2 & !is.na(years_since_first_hit), 1, 0),
         minus_one = ifelse(years_since_first_hit == -1 & !is.na(years_since_first_hit), 1, 0),
         plus_zero = ifelse(years_since_first_hit == 0 & !is.na(years_since_first_hit), 1, 0),
         plus_one = ifelse(years_since_first_hit == 1 & !is.na(years_since_first_hit), 1, 0),
         plus_two = ifelse(years_since_first_hit == 2 & !is.na(years_since_first_hit), 1, 0),
         plus_three = ifelse(years_since_first_hit == 3 & !is.na(years_since_first_hit), 1, 0),
         plus_four = ifelse(years_since_first_hit == 4 & !is.na(years_since_first_hit), 1, 0),
         plus_five = ifelse(years_since_first_hit == 5 & !is.na(years_since_first_hit), 1, 0),
         plus_six = ifelse(years_since_first_hit == 6 & !is.na(years_since_first_hit), 1, 0),
         plus_seven = ifelse(years_since_first_hit == 7 & !is.na(years_since_first_hit), 1, 0),
         plus_eight = ifelse(years_since_first_hit == 8 & !is.na(years_since_first_hit), 1, 0),
         plus_nine = ifelse(years_since_first_hit == 9 & !is.na(years_since_first_hit), 1, 0),
         plus_ten = ifelse(years_since_first_hit == 10 & !is.na(years_since_first_hit), 1, 0),
         plus_eleven = ifelse(years_since_first_hit == 11 & !is.na(years_since_first_hit), 1, 0),
         plus_twelve = ifelse(years_since_first_hit == 12 & !is.na(years_since_first_hit), 1, 0))





```

prep

```{r}

# cohort: year that exposure happened
global_flood_full <- global_flood_full %>% 
  mutate(cohort = ifelse(years_since_first_hit == 0, year, NA))  %>%
  group_by(tile_id) %>%
  arrange(tile_id, year) %>%
  fill(cohort) %>%
  group_by(tile_id) %>%
  arrange(tile_id, -year) %>%
  fill(cohort) %>%
  arrange(tile_id, year) %>%
  mutate(cohort = ifelse(is.na(cohort),Inf,cohort))

full_flood <- global_flood_full %>% select(tile_id, ECONOMY, urban, ECON_URBAN,
                                           INCOME_URBAN, INCOME_GRP,
                                           gdp_value, year, cohort) %>%
  setDT()


full_flood<- full_flood %>% mutate(gdp_value_log=log(gdp_value))



# Filter out cohorts that don't have sufficient pre-period data
valid_cohorts <- full_flood %>%
  group_by(tile_id) %>%
  mutate(has_preperiod = any(year == cohort - 1)) %>%
  filter(has_preperiod) %>%
  pull(cohort) %>%
  unique()

full_filtered_flood <- full_flood %>%
  filter(cohort %in% valid_cohorts)




```


### DID all data combined  

model

```{r}



#specify variables
varnames = list()
varnames$time_name = "year" 
varnames$outcome_name = "gdp_value_log"
varnames$cohort_name = "cohort"
varnames$id_name = "tile_id"


#varnames$covariate_names = "month" 


did = DiD(inputdata = full_filtered_flood, 
          varnames = varnames,
          base_event = -1,
          min_event = -5, 
          max_event = 10, parallel_cores = num_cores, control_group = "future-treated")

print(did$results_average)

coef_did_combined_flood <- tibble(did$results_average)



coef_did_combined_flood<-coef_did_combined_flood %>% mutate(ATT_perc=100*(exp(ATTe)-1), 
                         lower_perc=100*(exp(ATTe - 1.965 * ATTe_SE)-1),
                         upper_perc=100*(exp(ATTe + 1.965 * ATTe_SE)-1))



write_csv(coef_did_combined_flood, "/home/dmedgyesi/international/DID/results/tables/Flood_GDP_AllData_DID_tables.csv")



```

plot

```{r}



ggplot(coef_did_combined_flood, aes(x = EventTime, y = ATT_perc)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Flood Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) 


ggsave("/home/dmedgyesi/international/DID/results/DID_Flood_GDP_AllData.png", width = 11, height = 8, dpi = 300)




```





### DID by Economy

model 

```{r}


varnames = list()
varnames$time_name = "year" 
varnames$outcome_name = "gdp_value_log"
varnames$cohort_name = "cohort"
varnames$id_name = "tile_id"

# Store results in a list
did_results <- list()
did_results_cohort<- list()

# Get unique economy classes
economy_classes <- unique(full_filtered_flood$ECONOMY)

# Loop through economy classes
for (econ in economy_classes) {
  
  # Filter dataset for the current economy class
  filtered_data <- full_filtered_flood %>%
    filter(ECONOMY == econ)
  
  # Run DiD model
  did <- DiD(inputdata = filtered_data, 
             varnames = varnames, 
             base_event = -1,
             min_event = -5, 
             max_event = 10, parallel_cores = num_cores, control_group = "future-treated")
  
  # Store results with economy class label
  did_results[[econ]] <- tibble(economy = econ, did$results_average)
  did_results_cohort[[econ]]<- tibble(economy=econ, did$results_cohort)
}

# Combine all results into one dataframe
coef_did_econ_flood <- bind_rows(did_results)
coef_did_cohort_econ_flood <- bind_rows(did_results_cohort)


coef_did_econ_flood<-coef_did_econ_flood %>% mutate(ATT_perc=100*(exp(ATTe)-1), 
                         lower_perc=100*(exp(ATTe - 1.965 * ATTe_SE)-1),
                         upper_perc=100*(exp(ATTe + 1.965 * ATTe_SE)-1))



coef_did_cohort_econ_flood<-coef_did_cohort_econ_flood %>% mutate(ATT_perc=100*(exp(ATTge)-1), 
                         lower_perc=100*(exp(ATTge - 1.965 * ATTge_SE)-1),
                         upper_perc=100*(exp(ATTge + 1.965 * ATTge_SE)-1))



write_csv(coef_did_econ_flood, "/home/dmedgyesi/international/DID/results/tables/Flood_GDP_Econ_DID_tables.csv")


```

plot

```{r}

ggplot(coef_did_econ_flood, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Flood Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Flood_GDP_Econ.png", width = 11, height = 8, dpi = 300)





#Developed
coef_did_econ_flood_developed<- coef_did_econ_flood %>% filter(substr(economy,1,1) %in% c(1,2))

ggplot(coef_did_econ_flood_developed, aes(x = EventTime, y =ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Flood Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Flood_GDP_Econ_Developed.png", width = 11, height = 8, dpi = 300)



#Emerging
coef_did_econ_flood_emerge<- coef_did_econ_flood %>% filter(substr(economy,1,1) %in% c(3,4,5))

ggplot(coef_did_econ_flood_emerge, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin =lower_perc, 
                      ymax =upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Flood Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Flood_GDP_Econ_Emerge.png", width = 11, height = 8, dpi = 300)



#Developing
coef_did_econ_flood_not_develop<- coef_did_econ_flood %>% filter(substr(economy,1,1) %in% c(6,7))

ggplot(coef_did_econ_flood_not_develop, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Flood Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Flood_GDP_Econ_NotDevelop.png", width = 11, height = 8, dpi = 300)




```


select results

```{r}

flood_results_econ<- coef_did_econ_flood %>% filter(EventTime>=0) %>% mutate(YearsCAT=cut2(EventTime, cuts = c(0,4,7,10)))

flood_results_econ<- flood_results_econ %>% group_by(economy, YearsCAT) %>% mutate(flg=case_when(ATT_perc==min(ATT_perc)~T, TRUE~F)) %>% ungroup() %>% filter(flg==T)

vars<- c("ATTe", "ATTe_SE", "ATT_perc", "lower_perc", "upper_perc")

flood_results_econ <- flood_results_econ %>%
  mutate(across(all_of(vars), ~ ifelse(ATT_perc > 0, 0, .)))




ggplot(flood_results_econ, aes(x = YearsCAT, y = ATT_perc, color=economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the severe flood event occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class


ggsave("/home/dmedgyesi/international/DID/results/DID_Flood_GDP_Econ_FINAL.png", width = 11, height = 8, dpi = 300)





```


plot by cohort

```{r}

coef_did_cohort_econ_flood<- coef_did_cohort_econ_flood %>% 
  mutate(period=case_when(Cohort %in% 2003:2009~"2003-2009", 
                          Cohort %in% 2010:2016~"2010-2016", 
                          TRUE~"2017-2021"))

# Get unique economy classes
economy_classes <- unique(coef_did_cohort_econ_flood$economy)

# Loop through each economy class
for (econ in economy_classes) {
  
  # Filter data for the current economy class
  df_filtered <- coef_did_cohort_econ_flood %>% filter(economy == econ)
  
  # Create plot
  p <- ggplot(df_filtered, aes(x = EventTime, y = ATT_perc,shape=period, 
                               color =period)) +
    geom_pointrange(aes(ymin = lower_perc, ymax = upper_perc), linewidth = 0.25) +
    geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
    geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
    xlab("Years since the First Flood Event Occurred") +
    ylab("GDP Percentage Change, 95% C.I.") +
    theme_bw() +
    theme(plot.background = element_rect(fill = "white"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          axis.line.y = element_line(color = "black"),
          axis.line.x = element_line(color = "black")) +
    ggtitle(paste("GDP Impact -", econ))  # Add title for clarity

  # Define the file name dynamically
  file_name <- paste0("/home/dmedgyesi/international/DID/results/plot_cohort/DID_Flood_GDP_Econ_", econ, ".png")
  
  # Save the plot
  ggsave(file_name, plot = p, width = 6, height = 6, dpi = 300)
  }


```


### DID by Economy and Urbanicity 

model

```{r}



varnames = list()
varnames$time_name = "year" 
varnames$outcome_name = "gdp_value_log"
varnames$cohort_name = "cohort"
varnames$id_name = "tile_id"



# Store results in a list
did_results <- list()

# Get unique economy classes
economy_classes <- unique(full_filtered_flood$ECON_URBAN)

# Loop through economy classes
for (econ in economy_classes) {
  
  # Filter dataset for the current economy class
  filtered_data <- full_filtered_flood %>%
    filter(ECON_URBAN == econ)
  
  # Run DiD model
  did <- DiD(inputdata = filtered_data, 
             varnames = varnames, 
             base_event = -1,
             min_event = -5, 
             max_event = 10, parallel_cores = num_cores, control_group = "future-treated")
  
  # Store results with economy class label
  did_results[[econ]] <- tibble(economy = econ, did$results_average)
}

# Combine all results into one dataframe
coef_did_econurban_flood <- bind_rows(did_results)


coef_did_econurban_flood<-coef_did_econurban_flood %>% mutate(ATT_perc=100*(exp(ATTe)-1), 
                         lower_perc=100*(exp(ATTe - 1.965 * ATTe_SE)-1),
                         upper_perc=100*(exp(ATTe + 1.965 * ATTe_SE)-1))



write_csv(coef_did_econurban_flood, "/home/dmedgyesi/international/DID/results/tables/Flood_GDP_EconUrban_DID_tables.csv")



```

plot

```{r}


coef_did_econurban_flood<- coef_did_econurban_flood %>% 
  mutate(urban=str_sub(economy, start= -1), 
                              economy_only=str_sub(economy, start=1,end= -4)) %>% 
  mutate(economy_label=paste0(economy_only, ", ", ifelse(urban=="F", "Rural", "Urban"))) %>% 
  select(economy, economy_only, urban,economy_label, everything())

ggplot(coef_did_econurban_flood, aes(x = EventTime, y = ATT_perc, color = economy_only, shape = urban)) +
  geom_pointrange(aes(ymin =lower_perc, 
                      ymax =upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
   xlab("Years since the First Flood Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
   theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black"), 
        legend.position = "none") +
facet_wrap(~ economy_label, ncol=4) 

ggsave("/home/dmedgyesi/international/DID/results/DID_Flood_GDP_EconUrban.png", width = 11, height = 8, dpi = 300)


#Developed
coef_did_econurban_flood_developed<- coef_did_econurban_flood %>% filter(substr(economy,1,1) %in% c(1,2))

ggplot(coef_did_econurban_flood_developed, aes(x = EventTime, y =ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Flood Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Flood_GDP_EconUrban_Developed.png", width = 11, height = 8, dpi = 300)



#Emerging
coef_did_econurban_flood_emerge<- coef_did_econurban_flood %>% filter(substr(economy,1,1) %in% c(3,4,5))

ggplot(coef_did_econurban_flood_emerge, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin =lower_perc, 
                      ymax =upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Flood Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Flood_GDP_EconUrban_Emerge.png", width = 11, height = 8, dpi = 300)



#Developing
coef_did_econurban_flood_not_develop<- coef_did_econurban_flood %>% filter(substr(economy,1,1) %in% c(6,7))

ggplot(coef_did_econurban_flood_not_develop, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First Flood Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Flood_GDP_EconUrban_NotDevelop.png", width = 11, height = 8, dpi = 300)






```



select results

```{r}

flood_results<- coef_did_econurban_flood %>% filter(EventTime>=0) %>% mutate(YearsCAT=cut2(EventTime, cuts = c(0,4,7,10)))

flood_results<- flood_results %>% group_by(economy, YearsCAT) %>% mutate(flg=case_when(ATT_perc==min(ATT_perc)~T, TRUE~F)) %>% ungroup() %>% filter(flg==T)

vars<- c("ATTe", "ATTe_SE", "ATT_perc", "lower_perc", "upper_perc")

flood_results <- flood_results %>%
  mutate(across(all_of(vars), ~ ifelse(ATT_perc > 0, 0, .)))


flood_results<- flood_results %>% 
  mutate(type=case_when(urban=="T"~"urban", urban=="F"~"rural", TRUE~NA)) %>% 
  mutate(type=factor(type, levels = c("rural", "urban")))




ggplot(flood_results, aes(x = YearsCAT, y = ATT_perc, color = type, shape = type)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25,  position = position_dodge(width = 0.3)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the severe flood event occurred") +
  ylab("GDP Change (%), 95% CI") +
  theme_bw() +
  scale_x_discrete(labels=c("[ 0, 4)"="0-3", "[ 4, 7)"= "4-6", "[ 7,10]"="7-10"))+
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black"), 
        legend.title = element_blank()) +
  facet_wrap(~ economy_only)+  # Facet by economy class
 ggtitle("Severe Flood Event — GDP Change")

ggsave("/home/dmedgyesi/international/DID/results/DID_Flood_GDP_EconUrban_FINAL.png", width = 11, height = 8, dpi = 300)

```

For journal 

```{r}


flood_results<- flood_results %>% 
  mutate(type=factor(type, levels = c("urban", "rural")))

ggplot(flood_results, aes(x = YearsCAT, y = ATT_perc, fill = type)) +
  geom_col(position = position_dodge(width = 0.6), width = 0.5) +
  geom_errorbar(aes(ymin = lower_perc, ymax = upper_perc),
                position = position_dodge(width = 0.6),
                width = 0.2, linewidth = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the severe flood event occurred") +
  ylab("Max GDP Decline (%), 95% CI") +
  scale_x_discrete(labels = c("[ 0, 4)" = "0-3", "[ 4, 7)" = "4-6", "[ 7,10]" = "7-10")) +
  scale_fill_manual(values = c("rural" = "#F8766D", "urban" = "#00BFC4")) + 
  theme_bw() +
  theme(
    plot.background = element_rect(fill = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    axis.line.y = element_line(color = "black"),
    axis.line.x = element_line(color = "black"),
    legend.title = element_blank()
  ) +
  facet_wrap(~ economy_only) +
  ggtitle("Severe Flood Event — GDP Change")


ggsave("/home/dmedgyesi/international/DID/results/Fig4.png", width = 7, height = 5, dpi = 300)


ggsave("/home/dmedgyesi/international/DID/results/Fig4.eps", width = 7, height = 5)


flood_results_format<- flood_results %>% 
  mutate(`Percent Decrease (95% CI)`= paste0(sprintf("%.2f", ATT_perc), " (", 
                                             sprintf("%.2f", lower_perc), ", ", 
                                             sprintf("%.2f", upper_perc), ")")) %>% 
  select(economy_only, YearsCAT, type, `Percent Decrease (95% CI)`) %>% pivot_wider(
    names_from = type,
    values_from = `Percent Decrease (95% CI)`
  ) %>% arrange(economy_only)

write_csv(flood_results_format, "/home/dmedgyesi/international/DID/results/tables/Flood_GDP_EconUrban_DID_tables_3periods.csv")

```

# WIND



### Read and prep data 

```{r}

#wind
global_wind_all_years <- read.csv('/mnt/theia/implications/global_wind_exposure_v2/global_wind_all_first.csv')


global_wind_all_years <- global_wind_all_years %>% 
  mutate(cohort = ifelse(first_wind_event == 1, year, NA))  %>%
  group_by(tile_id) %>%
  arrange(tile_id, year) %>%
  fill(cohort, .direction = "downup") %>% ungroup() %>% 
  mutate(years_since_first_hit=year-cohort) %>% select(-cohort)

look<- global_wind_all_years %>% group_by(year) %>% summarise(sum(years_since_first_hit==1, na.rm=T))


# Merge datasets and clean them
global_wind_full <- inner_join(global_wind_all_years, 
                              final_gdp_df, by=c("tile_id","year"))



#drop those without gdp
global_wind_full <- global_wind_full %>%
  filter(!is.na(gdp_value)) 


length(unique(global_wind_full$tile_id))

count_obs_wind<- global_wind_full %>% 
  group_by(ECON_URBAN) %>% summarise(n_areas=length(unique(tile_id)), n_wind=sum(first_wind_event==1, na.rm = T))



# Make Event-Time Variables and Adjust for Inflation Sale Prices
global_wind_full <- global_wind_full %>%
  mutate(minus_seven = ifelse(years_since_first_hit <= -7 & !is.na(years_since_first_hit), 1, 0),
         minus_six = ifelse(years_since_first_hit == -6 & !is.na(years_since_first_hit), 1, 0),
         minus_five = ifelse(years_since_first_hit == -5 & !is.na(years_since_first_hit), 1, 0),
         minus_four = ifelse(years_since_first_hit == -4 & !is.na(years_since_first_hit), 1, 0),
         minus_three = ifelse(years_since_first_hit == -3 & !is.na(years_since_first_hit), 1, 0),
         minus_two = ifelse(years_since_first_hit == -2 & !is.na(years_since_first_hit), 1, 0),
         minus_one = ifelse(years_since_first_hit == -1 & !is.na(years_since_first_hit), 1, 0),
         plus_zero = ifelse(years_since_first_hit == 0 & !is.na(years_since_first_hit), 1, 0),
         plus_one = ifelse(years_since_first_hit == 1 & !is.na(years_since_first_hit), 1, 0),
         plus_two = ifelse(years_since_first_hit == 2 & !is.na(years_since_first_hit), 1, 0),
         plus_three = ifelse(years_since_first_hit == 3 & !is.na(years_since_first_hit), 1, 0),
         plus_four = ifelse(years_since_first_hit == 4 & !is.na(years_since_first_hit), 1, 0),
         plus_five = ifelse(years_since_first_hit == 5 & !is.na(years_since_first_hit), 1, 0),
         plus_six = ifelse(years_since_first_hit == 6 & !is.na(years_since_first_hit), 1, 0),
         plus_seven = ifelse(years_since_first_hit == 7 & !is.na(years_since_first_hit), 1, 0),
         plus_eight = ifelse(years_since_first_hit == 8 & !is.na(years_since_first_hit), 1, 0),
         plus_nine = ifelse(years_since_first_hit == 9 & !is.na(years_since_first_hit), 1, 0),
         plus_ten = ifelse(years_since_first_hit == 10 & !is.na(years_since_first_hit), 1, 0),
         plus_eleven = ifelse(years_since_first_hit == 11 & !is.na(years_since_first_hit), 1, 0),
         plus_twelve = ifelse(years_since_first_hit == 12 & !is.na(years_since_first_hit), 1, 0))


```


prep

```{r}

# cohort: year that exposure happened
global_wind_full <- global_wind_full %>% 
  mutate(cohort = ifelse(years_since_first_hit == 0, year, NA))  %>%
  group_by(tile_id) %>%
  arrange(tile_id, year) %>%
  fill(cohort) %>%
  group_by(tile_id) %>%
  arrange(tile_id, -year) %>%
  fill(cohort) %>%
  arrange(tile_id, year) %>%
  mutate(cohort = ifelse(is.na(cohort),Inf,cohort))

full_wind <- global_wind_full %>% select(tile_id, ECONOMY, urban, ECON_URBAN,
                                         INCOME_URBAN, INCOME_GRP,
                                         gdp_value, year, cohort) %>%
  setDT()


full_wind<- full_wind %>% mutate(gdp_value_log=log(gdp_value))



# Filter out cohorts that don't have sufficient pre-period data
valid_cohorts <- full_wind %>%
  group_by(tile_id) %>%
  mutate(has_preperiod = any(year == cohort - 1)) %>%
  filter(has_preperiod) %>%
  pull(cohort) %>%
  unique()

full_filtered_wind <- full_wind %>%
  filter(cohort %in% valid_cohorts)




```


### DID all data combined  

model

```{r}



#specify variables
varnames = list()
varnames$time_name = "year" 
varnames$outcome_name = "gdp_value_log"
varnames$cohort_name = "cohort"
varnames$id_name = "tile_id"


#varnames$covariate_names = "month" 


did = DiD(inputdata = full_filtered_wind, 
          varnames = varnames,
          base_event = -1,
          min_event = -5, 
          max_event = 10, parallel_cores = num_cores, control_group = "future-treated")

print(did$results_average)

coef_did_combined_wind <- tibble(did$results_average)



coef_did_combined_wind<-coef_did_combined_wind %>% mutate(ATT_perc=100*(exp(ATTe)-1), 
                         lower_perc=100*(exp(ATTe - 1.965 * ATTe_SE)-1),
                         upper_perc=100*(exp(ATTe + 1.965 * ATTe_SE)-1))



write_csv(coef_did_combined_wind, "/home/dmedgyesi/international/DID/results/tables/Wind_GDP_AllData_DID_tables.csv")



```

plot

```{r}



ggplot(coef_did_combined_wind, aes(x = EventTime, y = ATT_perc)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First wind Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) 


ggsave("/home/dmedgyesi/international/DID/results/DID_Wind_GDP_AllData.png", width = 11, height = 8, dpi = 300)




```





### DID by Economy

model 

```{r}


varnames = list()
varnames$time_name = "year" 
varnames$outcome_name = "gdp_value_log"
varnames$cohort_name = "cohort"
varnames$id_name = "tile_id"

# Store results in a list
did_results <- list()
did_results_cohort<- list()

# Get unique economy classes
economy_classes <- unique(full_filtered_wind$ECONOMY)

# Loop through economy classes
for (econ in economy_classes) {
  
  # Filter dataset for the current economy class
  filtered_data <- full_filtered_wind %>%
    filter(ECONOMY == econ)
  
  # Run DiD model
  did <- DiD(inputdata = filtered_data, 
             varnames = varnames, 
             base_event = -1,
             min_event = -5, 
             max_event = 10, parallel_cores = num_cores, control_group = "future-treated")
  
  # Store results with economy class label
  did_results[[econ]] <- tibble(economy = econ, did$results_average)
  did_results_cohort[[econ]]<- tibble(economy=econ, did$results_cohort)
}

# Combine all results into one dataframe
coef_did_econ_wind <- bind_rows(did_results)
coef_did_cohort_econ_wind <- bind_rows(did_results_cohort)



coef_did_econ_wind<-coef_did_econ_wind %>% mutate(ATT_perc=100*(exp(ATTe)-1), 
                         lower_perc=100*(exp(ATTe - 1.965 * ATTe_SE)-1),
                         upper_perc=100*(exp(ATTe + 1.965 * ATTe_SE)-1))


coef_did_cohort_econ_wind<-coef_did_cohort_econ_wind %>% mutate(ATT_perc=100*(exp(ATTge)-1), 
                         lower_perc=100*(exp(ATTge - 1.965 * ATTge_SE)-1),
                         upper_perc=100*(exp(ATTge + 1.965 * ATTge_SE)-1))



write_csv(coef_did_econ_wind, "/home/dmedgyesi/international/DID/results/tables/Wind_GDP_Econ_DID_tables.csv")


```

plot

```{r}

ggplot(coef_did_econ_wind, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First wind Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Wind_GDP_Econ.png", width = 11, height = 8, dpi = 300)





#Developed
coef_did_econ_wind_developed<- coef_did_econ_wind %>% filter(substr(economy,1,1) %in% c(1,2))

ggplot(coef_did_econ_wind_developed, aes(x = EventTime, y =ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First wind Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Wind_GDP_Econ_Developed.png", width = 11, height = 8, dpi = 300)



#Emerging
coef_did_econ_wind_emerge<- coef_did_econ_wind %>% filter(substr(economy,1,1) %in% c(3,4,5))

ggplot(coef_did_econ_wind_emerge, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin =lower_perc, 
                      ymax =upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First wind Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Wind_GDP_Econ_Emerge.png", width = 11, height = 8, dpi = 300)



#Developing
coef_did_econ_wind_not_develop<- coef_did_econ_wind %>% filter(substr(economy,1,1) %in% c(6,7))

ggplot(coef_did_econ_wind_not_develop, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First wind Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Wind_GDP_Econ_NotDevelop.png", width = 11, height = 8, dpi = 300)




```



select results

```{r}

wind_results_econ<- coef_did_econ_wind %>% filter(EventTime>=0) %>% mutate(YearsCAT=cut2(EventTime, cuts = c(0,4,7,10)))

wind_results_econ<- wind_results_econ %>% group_by(economy, YearsCAT) %>% mutate(flg=case_when(ATT_perc==min(ATT_perc)~T, TRUE~F)) %>% ungroup() %>% filter(flg==T)

vars<- c("ATTe", "ATTe_SE", "ATT_perc", "lower_perc", "upper_perc")

wind_results_econ <- wind_results_econ %>%
  mutate(across(all_of(vars), ~ ifelse(ATT_perc > 0, 0, .)))




ggplot(wind_results_econ, aes(x = YearsCAT, y = ATT_perc, color=economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the severe wind event occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class


ggsave("/home/dmedgyesi/international/DID/results/DID_Wind_GDP_Econ_FINAL.png", width = 11, height = 8, dpi = 300)





```



plot by cohort

```{r}

coef_did_cohort_econ_wind<- coef_did_cohort_econ_wind %>% 
  mutate(period=case_when(Cohort %in% 2003:2009~"2003-2009", 
                          Cohort %in% 2010:2016~"2010-2016", 
                          TRUE~"2017-2021"))

# Get unique economy classes
economy_classes <- unique(coef_did_cohort_econ_wind$economy)

# Loop through each economy class
for (econ in economy_classes) {
  
  # Filter data for the current economy class
  df_filtered <- coef_did_cohort_econ_wind %>% filter(economy == econ)
  
  # Create plot
  p <- ggplot(df_filtered, aes(x = EventTime, y = ATT_perc,shape=period, 
                               color =period)) +
    geom_pointrange(aes(ymin = lower_perc, ymax = upper_perc), linewidth = 0.25) +
    geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
    geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
    xlab("Years since the First Wind Event Occurred") +
    ylab("GDP Percentage Change, 95% C.I.") +
    theme_bw() +
    theme(plot.background = element_rect(fill = "white"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          axis.line.y = element_line(color = "black"),
          axis.line.x = element_line(color = "black")) +
    ggtitle(paste("GDP Impact -", econ))  # Add title for clarity

  # Define the file name dynamically
  file_name <- paste0("/home/dmedgyesi/international/DID/results/plot_cohort/DID_Wind_GDP_Econ_", econ, ".png")
  
  # Save the plot
  ggsave(file_name, plot = p, width = 6, height = 6, dpi = 300)
  }


```



### DID by Economy and Urbanicity 

model

```{r}



varnames = list()
varnames$time_name = "year" 
varnames$outcome_name = "gdp_value_log"
varnames$cohort_name = "cohort"
varnames$id_name = "tile_id"



# Store results in a list
did_results <- list()

# Get unique economy classes
economy_classes <- unique(full_filtered_wind$ECON_URBAN)

# Loop through economy classes
for (econ in economy_classes) {
  
  # Filter dataset for the current economy class
  filtered_data <- full_filtered_wind %>%
    filter(ECON_URBAN == econ)
  
  # Run DiD model
  did <- DiD(inputdata = filtered_data, 
             varnames = varnames, 
             base_event = -1,
             min_event = -5, 
             max_event = 10, parallel_cores = num_cores, control_group = "future-treated")
  
  # Store results with economy class label
  did_results[[econ]] <- tibble(economy = econ, did$results_average)
}

# Combine all results into one dataframe
coef_did_econurban_wind <- bind_rows(did_results)


coef_did_econurban_wind<-coef_did_econurban_wind %>% mutate(ATT_perc=100*(exp(ATTe)-1), 
                         lower_perc=100*(exp(ATTe - 1.965 * ATTe_SE)-1),
                         upper_perc=100*(exp(ATTe + 1.965 * ATTe_SE)-1))


write_csv(coef_did_econurban_wind, "/home/dmedgyesi/international/DID/results/tables/Wind_GDP_EconUrban_DID_tables.csv")



```

plot

```{r}


coef_did_econurban_wind<- coef_did_econurban_wind %>% 
  mutate(urban=str_sub(economy, start= -1), 
                              economy_only=str_sub(economy, start=1,end= -4)) %>% 
  mutate(economy_label=paste0(economy_only, ", ", ifelse(urban=="F", "Rural", "Urban"))) %>% 
  select(economy, economy_only, urban,economy_label, everything())

ggplot(coef_did_econurban_flood, aes(x = EventTime, y = ATT_perc, color = economy_only, shape = urban)) +
  geom_pointrange(aes(ymin =lower_perc, 
                      ymax =upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
   xlab("Years since the First Flood Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
   theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black"), 
        legend.position = "none") +
facet_wrap(~ economy_label, ncol=4) 


####

ggplot(coef_did_econurban_wind, aes(x = EventTime, y = ATT_perc, color = economy_only, shape = urban)) +
  geom_pointrange(aes(ymin =lower_perc, 
                      ymax =upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First wind Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
   theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black"), 
        legend.position = "none") +
facet_wrap(~ economy_label, ncol=4) 

ggsave("/home/dmedgyesi/international/DID/results/DID_Wind_GDP_EconUrban.png", width = 11, height = 8, dpi = 300)


#Developed
coef_did_econurban_wind_developed<- coef_did_econurban_wind %>% filter(substr(economy,1,1) %in% c(1,2))

ggplot(coef_did_econurban_wind_developed, aes(x = EventTime, y =ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First wind Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Wind_GDP_EconUrban_Developed.png", width = 11, height = 8, dpi = 300)



#Emerging
coef_did_econurban_wind_emerge<- coef_did_econurban_wind %>% filter(substr(economy,1,1) %in% c(3,4,5))

ggplot(coef_did_econurban_wind_emerge, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin =lower_perc, 
                      ymax =upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First wind Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Wind_GDP_EconUrban_Emerge.png", width = 11, height = 8, dpi = 300)



#Developing
coef_did_econurban_wind_not_develop<- coef_did_econurban_wind %>% filter(substr(economy,1,1) %in% c(6,7))

ggplot(coef_did_econurban_wind_not_develop, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First wind Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_Wind_GDP_EconUrban_NotDevelop.png", width = 11, height = 8, dpi = 300)






```

select results

```{r}


wind_results<- coef_did_econurban_wind %>% filter(EventTime>=0) %>% mutate(YearsCAT=cut2(EventTime, cuts = c(0,4,7,10)))

wind_results<- wind_results %>% group_by(economy, YearsCAT) %>% mutate(flg=case_when(ATT_perc==min(ATT_perc)~T, TRUE~F)) %>% ungroup() %>% filter(flg==T)

vars<- c("ATTe", "ATTe_SE", "ATT_perc", "lower_perc", "upper_perc")

wind_results <- wind_results %>%
  mutate(across(all_of(vars), ~ ifelse(ATT_perc > 0, 0, .)))



wind_results<- wind_results %>% 
  mutate(type=case_when(urban=="T"~"urban", urban=="F"~"rural", TRUE~NA)) %>% 
  mutate(type=factor(type, levels = c("rural", "urban")))


ggplot(wind_results, aes(x = YearsCAT, y = ATT_perc, color = type, shape = type)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25, position = position_dodge(width = 0.3)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the severe wind event occurred") +
 ylab("GDP Change (%), 95% CI") +
  theme_bw() +
  scale_x_discrete(labels=c("[ 0, 4)"="0-3", "[ 4, 7)"= "4-6", "[ 7,10]"="7-10"))+
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black"), 
        legend.title = element_blank()) +
  facet_wrap(~ economy_only)+  # Facet by economy class
 ggtitle("Severe Wind Event — GDP Change")


ggsave("/home/dmedgyesi/international/DID/results/DID_Wind_GDP_EconUrban_FINAL.png", width = 11, height = 8, dpi = 300)


wind_results_format<- wind_results %>% 
  mutate(`Percent Decrease (95% CI)`= paste0(sprintf("%.2f", ATT_perc), " (", 
                                             sprintf("%.2f", lower_perc), ", ", 
                                             sprintf("%.2f", upper_perc), ")")) %>% 
  select(economy_only, YearsCAT, type, `Percent Decrease (95% CI)`) %>% pivot_wider(
    names_from = type,
    values_from = `Percent Decrease (95% CI)`
  ) %>% arrange(economy_only)

write_csv(wind_results_format, "/home/dmedgyesi/international/DID/results/tables/Wind_GDP_EconUrban_DID_tables_3periods.csv")



```


### Save final results

```{r}


### select results 

econ_levels <- sort(unique(final_gdp_df$ECONOMY))

econ_levels

### FIRE 

select_econ<- econ_levels[c(3,4,6,7)]

select_econ_urban<- econ_levels[econ_levels %!in% select_econ]


fire_results_econ_select<- fire_results_econ %>% 
  filter(economy %in% select_econ) %>% 
  mutate(urban="overall") %>% select(economy, urban, everything())

fire_results_econurban_select<- fire_results %>% 
  filter(economy_only %in% select_econ_urban) %>% 
  select(-c(economy, economy_label, type)) %>% rename(economy=economy_only)

fire_results_combined<- rbind(fire_results_econ_select, fire_results_econurban_select)

fire_results_combined<- fire_results_combined %>% mutate(exposure="fire")

### FLOOD

select_econ<- econ_levels[c(2,4,5,6)]

select_econ_urban<- econ_levels[econ_levels %!in% select_econ]


flood_results_econ_select<- flood_results_econ %>% 
  filter(economy %in% select_econ) %>% 
  mutate(urban="overall") %>% select(economy, urban, everything())

flood_results_econurban_select<- flood_results %>% 
  filter(economy_only %in% select_econ_urban) %>% 
  select(-c(economy, economy_label, type)) %>% rename(economy=economy_only)

flood_results_combined<- rbind(flood_results_econ_select, flood_results_econurban_select)

flood_results_combined<- flood_results_combined %>% mutate(exposure="flood")


### WIND 
select_econ<- econ_levels[c(2,3,4,5)]

select_econ_urban<- econ_levels[econ_levels %!in% select_econ]


wind_results_econ_select<- wind_results_econ %>% 
  filter(economy %in% select_econ) %>% 
  mutate(urban="overall") %>% select(economy, urban, everything())

wind_results_econurban_select<- wind_results %>% 
  filter(economy_only %in% select_econ_urban) %>% 
  select(-c(economy, economy_label, type)) %>% rename(economy=economy_only)

wind_results_combined<- rbind(wind_results_econ_select, wind_results_econurban_select)

wind_results_combined<- wind_results_combined %>% mutate(exposure="wind")

### PULL TOGETHER

gdp_results_all_exposures<- fire_results_combined %>% rbind(flood_results_combined) %>% rbind(wind_results_combined)


colnames(gdp_results_all_exposures)

gdp_results_all_exposures<- gdp_results_all_exposures %>% 
  select(exposure, economy:urban, YearsCAT, EventTime, ATTe, ATTe_SE) %>% 
  mutate(DiD_gdp_change_estimate=(exp(ATTe)-1), 
         DiD_gdp_change_se=exp(ATTe)*ATTe_SE,
                         DiD_gdp_lower=DiD_gdp_change_estimate - 1.965 * DiD_gdp_change_se,
                         DiD_gdp_upper=DiD_gdp_change_estimate + 1.965 * DiD_gdp_change_se) %>% 
  rename(ECONOMY=economy)



write_csv(gdp_results_all_exposures, "/home/dmedgyesi/international/DID/results/tables/Select_Results_GDP_DID_tables.csv")


```


#### EXTRAAA

# FLOOD 20yr



### Read and prep data 

```{r}

#fire
global_flood20yr_all_years <- read.csv('/mnt/theia/implications/global_flood_exposure/global_flood_all_first.csv')


# Merge datasets and clean them
global_flood20yr_full <- left_join(global_flood20yr_all_years, 
                               final_gdp_df, by=c("tile_id","year"))


#Econ and Urban flag
global_flood20yr_full<- global_flood20yr_full %>% mutate(ECON_URBAN=paste0(ECONOMY, ", ",urban))


#drop those without gdp
global_flood20yr_full <- global_flood20yr_full %>%
  filter(!is.na(gdp_value)) 


length(unique(global_flood20yr_full$tile_id))

count_obs_flood20yr<- global_flood20yr_full %>% 
  group_by(ECON_URBAN) %>% summarise(n_areas=length(unique(tile_id)), n_flood=sum(first_flood_event==1, na.rm = T))



# Make Event-Time Variables and Adjust for Inflation Sale Prices
global_flood20yr_full <- global_flood20yr_full %>%
  mutate(minus_seven = ifelse(years_since_first_hit <= -7 & !is.na(years_since_first_hit), 1, 0),
         minus_six = ifelse(years_since_first_hit == -6 & !is.na(years_since_first_hit), 1, 0),
         minus_five = ifelse(years_since_first_hit == -5 & !is.na(years_since_first_hit), 1, 0),
         minus_four = ifelse(years_since_first_hit == -4 & !is.na(years_since_first_hit), 1, 0),
         minus_three = ifelse(years_since_first_hit == -3 & !is.na(years_since_first_hit), 1, 0),
         minus_two = ifelse(years_since_first_hit == -2 & !is.na(years_since_first_hit), 1, 0),
         minus_one = ifelse(years_since_first_hit == -1 & !is.na(years_since_first_hit), 1, 0),
         plus_zero = ifelse(years_since_first_hit == 0 & !is.na(years_since_first_hit), 1, 0),
         plus_one = ifelse(years_since_first_hit == 1 & !is.na(years_since_first_hit), 1, 0),
         plus_two = ifelse(years_since_first_hit == 2 & !is.na(years_since_first_hit), 1, 0),
         plus_three = ifelse(years_since_first_hit == 3 & !is.na(years_since_first_hit), 1, 0),
         plus_four = ifelse(years_since_first_hit == 4 & !is.na(years_since_first_hit), 1, 0),
         plus_five = ifelse(years_since_first_hit == 5 & !is.na(years_since_first_hit), 1, 0),
         plus_six = ifelse(years_since_first_hit == 6 & !is.na(years_since_first_hit), 1, 0),
         plus_seven = ifelse(years_since_first_hit == 7 & !is.na(years_since_first_hit), 1, 0),
         plus_eight = ifelse(years_since_first_hit == 8 & !is.na(years_since_first_hit), 1, 0),
         plus_nine = ifelse(years_since_first_hit == 9 & !is.na(years_since_first_hit), 1, 0),
         plus_ten = ifelse(years_since_first_hit == 10 & !is.na(years_since_first_hit), 1, 0),
         plus_eleven = ifelse(years_since_first_hit == 11 & !is.na(years_since_first_hit), 1, 0),
         plus_twelve = ifelse(years_since_first_hit == 12 & !is.na(years_since_first_hit), 1, 0))





```


### DID all data combined  

prep

```{r}

# cohort: year that exposure happened
global_flood20yr_full <- global_flood20yr_full %>% 
  mutate(cohort = ifelse(years_since_first_hit == 0, year, NA))  %>%
  group_by(tile_id) %>%
  arrange(tile_id, year) %>%
  fill(cohort) %>%
  group_by(tile_id) %>%
  arrange(tile_id, -year) %>%
  fill(cohort) %>%
  arrange(tile_id, year) %>%
  mutate(cohort = ifelse(is.na(cohort),Inf,cohort))

full_flood20yr <- global_flood20yr_full %>% select(tile_id, ECONOMY, urban, ECON_URBAN,gdp_value, year, cohort) %>%
  setDT()


full_flood20yr<- full_flood20yr %>% mutate(gdp_value_log=log(gdp_value))



# Filter out cohorts that don't have sufficient pre-period data
valid_cohorts <- full_flood20yr %>%
  group_by(tile_id) %>%
  mutate(has_preperiod = any(year == cohort - 1)) %>%
  filter(has_preperiod) %>%
  pull(cohort) %>%
  unique()

full_filtered_flood20yr <- full_flood20yr %>%
  filter(cohort %in% valid_cohorts)




```

model

```{r}



#specify variables
varnames = list()
varnames$time_name = "year" 
varnames$outcome_name = "gdp_value_log"
varnames$cohort_name = "cohort"
varnames$id_name = "tile_id"


#varnames$covariate_names = "month" 


did = DiD(inputdata = full_filtered_flood20yr, 
          varnames = varnames,
          base_event = -1,
          min_event = -7, 
          max_event = 12, parallel_cores = num_cores, control_group = "future-treated")

print(did$results_average)

coef_did_combined_flood20yr <- tibble(did$results_average)



coef_did_combined_flood20yr<-coef_did_combined_flood20yr %>% mutate(ATT_perc=100*(exp(ATTe)-1), 
                                                            lower_perc=100*(exp(ATTe - 1.965 * ATTe_SE)-1),
                                                            upper_perc=100*(exp(ATTe + 1.965 * ATTe_SE)-1))



write_csv(coef_did_combined_flood20yr, "/home/dmedgyesi/international/DID/results/tables/flood20yr_GDP_AllData_DID_tables.csv")



```

plot

```{r}



ggplot(coef_did_combined_flood20yr, aes(x = EventTime, y = ATT_perc)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First flood20yr Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) 


ggsave("/home/dmedgyesi/international/DID/results/DID_flood20yr_GDP_AllData.png", width = 11, height = 8, dpi = 300)




```





### DID by Economy

model 

```{r}


varnames = list()
varnames$time_name = "year" 
varnames$outcome_name = "gdp_value_log"
varnames$cohort_name = "cohort"
varnames$id_name = "tile_id"

# Store results in a list
did_results <- list()
did_results_cohort<- list()

# Get unique economy classes
economy_classes <- unique(full_filtered_flood20yr$ECONOMY)

# Loop through economy classes
for (econ in economy_classes) {
  
  # Filter dataset for the current economy class
  filtered_data <- full_filtered_flood20yr %>%
    filter(ECONOMY == econ)
  
  # Run DiD model
  did <- DiD(inputdata = filtered_data, 
             varnames = varnames, 
             base_event = -1,
             min_event = -7, 
             max_event = 12, parallel_cores = num_cores, control_group = "future-treated")
  
  # Store results with economy class label
  did_results[[econ]] <- tibble(economy = econ, did$results_average)
  did_results_cohort[[econ]]<- tibble(economy=econ, did$results_cohort)
}

# Combine all results into one dataframe
coef_did_econ_flood20yr <- bind_rows(did_results)
coef_did_cohort_econ_flood20yr <- bind_rows(did_results_cohort)


coef_did_econ_flood20yr<-coef_did_econ_flood20yr %>% mutate(ATT_perc=100*(exp(ATTe)-1), 
                                                    lower_perc=100*(exp(ATTe - 1.965 * ATTe_SE)-1),
                                                    upper_perc=100*(exp(ATTe + 1.965 * ATTe_SE)-1))



coef_did_cohort_econ_flood20yr<-coef_did_cohort_econ_flood20yr %>% mutate(ATT_perc=100*(exp(ATTge)-1), 
                                                                  lower_perc=100*(exp(ATTge - 1.965 * ATTge_SE)-1),
                                                                  upper_perc=100*(exp(ATTge + 1.965 * ATTge_SE)-1))



write_csv(coef_did_econ_flood20yr, "/home/dmedgyesi/international/DID/results/tables/flood20yr_GDP_Econ_DID_tables.csv")


```

plot

```{r}

ggplot(coef_did_econ_flood20yr, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First flood20yr Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_flood20yr_GDP_Econ.png", width = 11, height = 8, dpi = 300)





#Developed
coef_did_econ_flood20yr_developed<- coef_did_econ_flood20yr %>% filter(substr(economy,1,1) %in% c(1,2))

ggplot(coef_did_econ_flood20yr_developed, aes(x = EventTime, y =ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First flood20yr Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_flood20yr_GDP_Econ_Developed.png", width = 11, height = 8, dpi = 300)



#Emerging
coef_did_econ_flood20yr_emerge<- coef_did_econ_flood20yr %>% filter(substr(economy,1,1) %in% c(3,4,5))

ggplot(coef_did_econ_flood20yr_emerge, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin =lower_perc, 
                      ymax =upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First flood20yr Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_flood20yr_GDP_Econ_Emerge.png", width = 11, height = 8, dpi = 300)



#Developing
coef_did_econ_flood20yr_not_develop<- coef_did_econ_flood20yr %>% filter(substr(economy,1,1) %in% c(6,7))

ggplot(coef_did_econ_flood20yr_not_develop, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First flood20yr Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_flood20yr_GDP_Econ_NotDevelop.png", width = 11, height = 8, dpi = 300)




```




plot by cohort

```{r}

coef_did_cohort_econ_flood20yr<- coef_did_cohort_econ_flood20yr %>% 
  mutate(period=case_when(Cohort %in% 2003:2009~"2003-2009", 
                          Cohort %in% 2010:2016~"2010-2016", 
                          TRUE~"2017-2021"))

# Get unique economy classes
economy_classes <- unique(coef_did_cohort_econ_flood20yr$economy)

# Loop through each economy class
for (econ in economy_classes) {
  
  # Filter data for the current economy class
  df_filtered <- coef_did_cohort_econ_flood20yr %>% filter(economy == econ)
  
  # Create plot
  p <- ggplot(df_filtered, aes(x = EventTime, y = ATT_perc,shape=period, 
                               color =period)) +
    geom_pointrange(aes(ymin = lower_perc, ymax = upper_perc), linewidth = 0.25) +
    geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
    geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
    xlab("Years since the First flood20yr Event Occurred") +
    ylab("GDP Percentage Change, 95% C.I.") +
    theme_bw() +
    theme(plot.background = element_rect(fill = "white"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          axis.line.y = element_line(color = "black"),
          axis.line.x = element_line(color = "black")) +
    ggtitle(paste("GDP Impact -", econ))  # Add title for clarity
  
  # Define the file name dynamically
  file_name <- paste0("/home/dmedgyesi/international/DID/results/plot_cohort/DID_flood20yr_GDP_Econ_", econ, ".png")
  
  # Save the plot
  ggsave(file_name, plot = p, width = 6, height = 6, dpi = 300)
}


```


### DID by Economy and Urbanicity 

model

```{r}



varnames = list()
varnames$time_name = "year" 
varnames$outcome_name = "gdp_value_log"
varnames$cohort_name = "cohort"
varnames$id_name = "tile_id"



# Store results in a list
did_results <- list()

# Get unique economy classes
economy_classes <- unique(full_filtered_flood20yr$ECON_URBAN)

# Loop through economy classes
for (econ in economy_classes) {
  
  # Filter dataset for the current economy class
  filtered_data <- full_filtered_flood20yr %>%
    filter(ECON_URBAN == econ)
  
  # Run DiD model
  did <- DiD(inputdata = filtered_data, 
             varnames = varnames, 
             base_event = -1,
             min_event = -7, 
             max_event = 12, parallel_cores = num_cores, control_group = "future-treated")
  
  # Store results with economy class label
  did_results[[econ]] <- tibble(economy = econ, did$results_average)
}

# Combine all results into one dataframe
coef_did_econurban_flood20yr <- bind_rows(did_results)


coef_did_econurban_flood20yr<-coef_did_econurban_flood20yr %>% mutate(ATT_perc=100*(exp(ATTe)-1), 
                                                              lower_perc=100*(exp(ATTe - 1.965 * ATTe_SE)-1),
                                                              upper_perc=100*(exp(ATTe + 1.965 * ATTe_SE)-1))



write_csv(coef_did_econurban_flood20yr, "/home/dmedgyesi/international/DID/results/tables/flood20yr_GDP_EconUrban_DID_tables.csv")



```

plot

```{r}

ggplot(coef_did_econurban_flood20yr, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin =lower_perc, 
                      ymax =upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First flood20yr Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_flood20yr_GDP_EconUrban.png", width = 11, height = 8, dpi = 300)


#Developed
coef_did_econurban_flood20yr_developed<- coef_did_econurban_flood20yr %>% filter(substr(economy,1,1) %in% c(1,2))

ggplot(coef_did_econurban_flood20yr_developed, aes(x = EventTime, y =ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First flood20yr Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_flood20yr_GDP_EconUrban_Developed.png", width = 11, height = 8, dpi = 300)



#Emerging
coef_did_econurban_flood20yr_emerge<- coef_did_econurban_flood20yr %>% filter(substr(economy,1,1) %in% c(3,4,5))

ggplot(coef_did_econurban_flood20yr_emerge, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin =lower_perc, 
                      ymax =upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First flood20yr Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_flood20yr_GDP_EconUrban_Emerge.png", width = 11, height = 8, dpi = 300)



#Developing
coef_did_econurban_flood20yr_not_develop<- coef_did_econurban_flood20yr %>% filter(substr(economy,1,1) %in% c(6,7))

ggplot(coef_did_econurban_flood20yr_not_develop, aes(x = EventTime, y = ATT_perc, color = economy)) +
  geom_pointrange(aes(ymin = lower_perc, 
                      ymax = upper_perc),
                  linewidth = 0.25) +
  #scale_y_continuous(labels = scales::percent,
  #                  breaks = c(-10.725, -5.1, -1.075, -0.05, -0.025, -0.125)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "grey", size = 0.5) +
  geom_vline(aes(xintercept = -1), linetype = "dashed", color = "grey", size = 0.5) +
  xlab("Years since the First flood20yr Event Occurred") +
  ylab("GDP Percentage Change, 95% C.I.") +
  theme_bw() +
  theme(plot.background = element_rect(fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line.y = element_line(color = "black"),
        axis.line.x = element_line(color = "black")) +
  facet_wrap(~ economy)  # Facet by economy class

ggsave("/home/dmedgyesi/international/DID/results/DID_flood20yr_GDP_EconUrban_NotDevelop.png", width = 11, height = 8, dpi = 300)






```






