---
title: "2-global_implications_data_prep"
output: html_document
date: "2024-10-28"
---

```{r setup, include=FALSE}

library(data.table)
library(readr)
library(ggplot2)
library(Hmisc)
library(haven)
library(patchwork)
library(mgcv)
library(dplyr)
library(tidyr)
library(stringr)
library(httr)

```

```{r}


global_dat<- readRDS("/mnt/theia/implications/dmed_global_data/Global Implications Datasets/global_dat.rds")

colnames(global_dat)


```


```{r}

# 
# countries <- st_read('/mnt/theia/implications/zhirsch/fs/international/intl_countries_shp/ne_10m_admin_0_countries.shp')
# 
# 
# countries<- countries %>% st_drop_geometry()
# 
# countries<- countries %>% mutate(ISO_A3=case_when(ISO_A3=="-99"~ADM0_A3, TRUE~ISO_A3))
# 
# ISO_NAME<- countries %>% select(ISO_A3, NAME, ECONOMY, SUBREGION, REGION_WB, REGION_UN,INCOME_GRP)
# 
# write_csv(ISO_NAME, "/mnt/theia/implications/dmed_global_data/ISO_KEY.csv")


```

```{r}


ISOkey<- read_csv("/mnt/theia/implications/dmed_global_data/ISO_KEY.csv")


global_dat<- ISOkey %>% right_join(global_dat, by=c("ISO_A3"="cntry_d"))



```

### Population change 

2000 to 2020 

```{r}


summary(global_dat$pop_00)
summary(global_dat$pop_20)


#remove NA's 
#should be no NA's

global_dat<- global_dat %>% filter(!is.na(pop_00))

#more than 10 people in 2000 

global_dat %>% group_by(pop_00>=10, pop_20>=10) %>% summarise(n())

global_dat<- global_dat %>% filter(pop_00>=10 & pop_20>=10) 


global_dat<- global_dat %>% 
  mutate(POP_CHANGE=round((pop_20-pop_00)/pop_00,4)) %>% 
  mutate(POP_CHANGE=ifelse(is.nan(POP_CHANGE)| is.infinite(POP_CHANGE), NA, POP_CHANGE))


summary(global_dat$POP_CHANGE)

quantile(global_dat$POP_CHANGE, probs = 0.01, na.rm = TRUE)

quantile(global_dat$POP_CHANGE, probs = 0.99, na.rm = TRUE)

##trim percentiles by subregion

trim_cats<- global_dat %>% group_by(SUBREGION) %>% 
  summarise(n(), n.notmiss=sum(!is.na(POP_CHANGE)),
            `0.01`=quantile(POP_CHANGE, probs = 0.01, na.rm = TRUE), 
            `0.99`=quantile(POP_CHANGE, probs = 0.99, na.rm = TRUE), 
            min=min(POP_CHANGE, na.rm = T), 
            max=max(POP_CHANGE, na.rm = T))



global_dat<- global_dat %>% group_by(SUBREGION) %>% 
  mutate(POP_CHANGE=case_when(POP_CHANGE<quantile(POP_CHANGE, probs=0.01, na.rm=T)~NA_real_, 
                              POP_CHANGE>quantile(POP_CHANGE, probs=0.99, na.rm=T)~NA_real_,
                              TRUE~POP_CHANGE)) %>% ungroup()
           



trim_cats<- global_dat %>% group_by(SUBREGION) %>% 
  summarise(n(),  n.notmiss=sum(!is.na(POP_CHANGE)),
            min=min(POP_CHANGE, na.rm = TRUE), 
            max=max(POP_CHANGE,  na.rm = TRUE))


global_dat %>% group_by(!is.na(POP_CHANGE)) %>% summarise(n())

global_dat<- global_dat %>% filter(!is.na(POP_CHANGE))


```



### HDI 

```{r}

summary(global_dat$hdi_2021)
summary(global_dat$hdi_2012)

```

```{r}
# 
# 
# hdi_dat<- global_dat %>%
#   select(tile_id, hdi_2012:hdi_2021) %>%
#   mutate(hdi_interp_2000=NA,
#          hdi_interp_2001=NA,
#          hdi_interp_2002=NA,
#          hdi_interp_2003=NA,
#          hdi_interp_2004=NA,
#          hdi_interp_2005=NA,
#          hdi_interp_2006=NA,
#          hdi_interp_2007=NA,
#          hdi_interp_2008=NA,
#          hdi_interp_2009=NA,
#          hdi_interp_2010=NA,
#          hdi_interp_2011=NA
#          ) %>%
#   select(tile_id, hdi_interp_2000:hdi_interp_2011, hdi_2012:hdi_2021) %>%
#   filter(!is.nan(hdi_2021))
# 
# #interpolated missing years 
# 
# hdi_dat_t<- as.data.frame(t(hdi_dat[,-c(1)]))
# 
# colnames(hdi_dat_t)<- hdi_dat$tile_id
# 
# tile_id<- colnames(hdi_dat_t)
# 
# 
# interpolate_hdi <- list()
# 
# for (i in 1:length(tile_id)) {
#   
#   dat <- data.frame(hdi = hdi_dat_t[, i], year = 2000:2021)
#   
#   # Identify the first and last years with actual data
#   first_year <- min(dat$year[!is.na(dat$hdi)], na.rm = TRUE)
#   last_year <- max(dat$year[!is.na(dat$hdi)], na.rm = TRUE)
#   
#   # Extract hdi values at those years
#   first_val <- dat$hdi[dat$year == first_year]
#   last_val <- dat$hdi[dat$year == last_year]
#   
#   # Fit a linear model
#   mod <- lm(log(hdi) ~ year, data = dat)
#   coef_slope <- coef(mod)["year"]  # Extract slope (rate of change)
#   
#   # Interpolate missing values using the estimated slope
#   dat <- dat %>%
#     mutate(
#       pred = case_when(
#         is.na(hdi) & year < first_year ~ exp(log(first_val) - coef_slope * (first_year - year)),  # Extrapolate before first data point
#         is.na(hdi) & year > last_year  ~ exp(log(last_val) + coef_slope * (year - last_year)),   # Extrapolate after last data point
#         is.na(hdi) ~ exp(log(first_val) + coef_slope * (year - first_year)),  # Interpolation between first & last observed values
#         TRUE ~ hdi
#       )
#     ) %>%
#     select(pred)
#   
#   colnames(dat) <- tile_id[i]
#   interpolate_hdi[[i]] <- dat
# }
# 
# # Combine interpolated columns
# interpolate_hdi_df <- do.call(cbind, interpolate_hdi)
# 
# 
# 
# interpolate_hdi_df<- as.data.frame(t(interpolate_hdi_df))
# 
# colnames(interpolate_hdi_df)<- colnames(hdi_dat[,-c(1)])
# 
# interpolate_hdi_df$tile_id<- as.numeric(rownames(interpolate_hdi_df))
#  
# interpolate_hdi_df<- interpolate_hdi_df %>% select(tile_id, everything())
#  
# 
# saveRDS(interpolate_hdi_df, file = "/home/dmedgyesi/international/data/global_implications_data/interpolate_hdi_df.rds")
# 
# 
# 

```




```{r}

interpolate_hdi_df<- readRDS("/home/dmedgyesi/international/data/global_implications_data/interpolate_hdi_df.rds")


interpolate_hdi_df<- interpolate_hdi_df %>% select(tile_id, hdi_interp_2000:hdi_interp_2011)


global_dat<- global_dat %>% left_join(interpolate_hdi_df, by="tile_id")



#global_dat<- global_dat %>% 
 # select(tile_id:gdp_pc_2022, hdi_interp_2000:hdi_interp_2011, everything())

```


```{r}

#interpolated
global_dat<- global_dat %>% 
  mutate(HDI_CHANGE_INT_00=round((hdi_2021-hdi_interp_2000)/hdi_interp_2000,4)) %>% 
  mutate(HDI_CHANGE_INT_00=ifelse(is.nan(HDI_CHANGE_INT_00)| is.infinite(HDI_CHANGE_INT_00), NA, HDI_CHANGE_INT_00))

global_dat<- global_dat %>% 
  mutate(HDI_DIFF_INT_00=round((hdi_2021-hdi_interp_2000),4)) %>% 
  mutate(HDI_DIFF_INT_00=ifelse(is.nan(HDI_DIFF_INT_00)| is.infinite(HDI_DIFF_INT_00), NA, HDI_DIFF_INT_00))



summary(global_dat$HDI_CHANGE_INT_00)
summary(global_dat$HDI_DIFF_INT_00)


quantile(global_dat$HDI_CHANGE_INT_00, seq(0,1,0.01), na.rm = TRUE)


look<- global_dat %>% 
  select(ISO_A3, NAME,HDI_CHANGE_INT_00)


min(global_dat$HDI_CHANGE_INT_00, na.rm = T)
max(global_dat$HDI_CHANGE_INT_00, na.rm = T)

#not interpolated
global_dat<- global_dat %>% 
  mutate(HDI_CHANGE=round((hdi_2021-hdi_2012)/hdi_2012,4)) %>% 
  mutate(HDI_DIFF=round((hdi_2021-hdi_2012),4)) %>% 
  mutate(HDI_CHANGE=ifelse(is.nan(HDI_CHANGE)| is.infinite(HDI_CHANGE), NA, HDI_CHANGE)) %>% 
  mutate(HDI_DIFF=ifelse(is.nan(HDI_DIFF)| is.infinite(HDI_DIFF), NA, HDI_DIFF))



summary(global_dat$HDI_CHANGE)


quantile(global_dat$HDI_CHANGE, seq(0,1,0.01), na.rm = TRUE)


table(is.na(global_dat$HDI_CHANGE))

```



### GDP 

```{r}
#evalute trends

summary(global_dat$GDP2000)
summary(global_dat$GDP2019)

# Summarize the GDP columns
summary_GDP <- global_dat %>%
  summarise(across(GDP2000:GDP2020, sum, na.rm = TRUE)) %>%
  pivot_longer(cols = everything(), names_to = "Year", values_to = "Sum_GDP")

# Clean up year column to remove "GDP_" prefix and convert to numeric
summary_GDP$Year <- as.numeric(sub("GDP", "", summary_GDP$Year))

# Plot the summarized data
ggplot(summary_GDP, aes(x = Year, y = Sum_GDP)) +
  geom_line(color = "blue") +
  geom_point(color = "red") +
  labs(title = "GDP Over Time", x = "Year", y = "GDP") +
  theme_minimal()

```



```{r}

###gdp trimming 

variables <- paste0("GDP", 2000:2020)


# Apply outlier filtering for each variable within groups
global_dat <- global_dat %>% 
  group_by(ECONOMY) %>% 
  mutate(across(all_of(variables), 
                ~ case_when(
                  . < quantile(., probs = 0.01, na.rm = TRUE) ~ NA_real_,
                  . > quantile(., probs = 0.99, na.rm = TRUE) ~ NA_real_,
                  TRUE ~ .
                ), 
                .names = "{.col}")) %>% 
  ungroup()




```




```{r}

global_dat <- global_dat %>%
  mutate(
    GDP_00_02 = rowMeans(select(., GDP2000, GDP2001, GDP2002), na.rm = TRUE),
    GDP_17_19 = rowMeans(select(., GDP2017, GDP2018, GDP2019), na.rm = TRUE)
  )


global_dat<- global_dat %>% 
  mutate(GDP_CHANGE=round((GDP_17_19-GDP_00_02)/GDP_00_02,4)) %>% 
  mutate(GDP_CHANGE=ifelse(is.nan(GDP_CHANGE)| is.infinite(GDP_CHANGE), NA, GDP_CHANGE))


summary(global_dat$GDP_CHANGE)


quantile(global_dat$GDP_CHANGE, seq(0,1,0.01), na.rm = TRUE)


##trim 0.01 and 0.99 percentiles by Economy

trim_cats<- global_dat %>% group_by(ECONOMY) %>% 
  summarise(n(), n.notmiss=sum(!is.na(GDP_CHANGE)),
            `0.01`=quantile(GDP_CHANGE, probs = 0.01, na.rm = TRUE), 
            `0.99`=quantile(GDP_CHANGE, probs = 0.99, na.rm = TRUE))



global_dat<- global_dat %>% group_by(ECONOMY) %>% 
  mutate(GDP_CHANGE=case_when(GDP_CHANGE<quantile(GDP_CHANGE, probs=0.01, na.rm=T)~NA_real_, 
                              GDP_CHANGE>quantile(GDP_CHANGE, probs=0.99, na.rm=T)~NA_real_,
                              TRUE~GDP_CHANGE)) %>% ungroup()
           



global_dat %>% group_by(ECONOMY) %>% 
  summarise(n(),  n.notmiss=sum(!is.na(GDP_CHANGE)),
            min=min(GDP_CHANGE, na.rm = TRUE), 
            max=max(GDP_CHANGE,  na.rm = TRUE))


quantile(global_dat$GDP_CHANGE, seq(0,1,0.01), na.rm = TRUE)


table(is.na(global_dat$GDP_CHANGE))

```



### GDP per capita


```{r}

global_dat <- global_dat %>%
  mutate(
    GDP_PC_00_02 = rowMeans(select(., gdp_pc_2000, gdp_pc_2001, gdp_pc_2002), na.rm = TRUE),
    GDP_PC_17_19 = rowMeans(select(., gdp_pc_2017, gdp_pc_2018, gdp_pc_2019), na.rm = TRUE)
  )


global_dat<- global_dat %>% 
  mutate(GDP_PC_CHANGE=round((GDP_PC_17_19-GDP_PC_00_02)/GDP_PC_00_02,4)) %>% 
  mutate(GDP_PC_CHANGE=ifelse(is.nan(GDP_PC_CHANGE)| is.infinite(GDP_PC_CHANGE), NA, GDP_PC_CHANGE))


summary(global_dat$GDP_PC_CHANGE)


quantile(global_dat$GDP_PC_CHANGE, seq(0,1,0.01), na.rm = TRUE)


##trim 0.01 and 0.99 percentiles by Economy

trim_cats<- global_dat %>% group_by(ECONOMY) %>% 
  summarise(n(), n.notmiss=sum(!is.na(GDP_PC_CHANGE)),
            `0.01`=quantile(GDP_PC_CHANGE, probs = 0.01, na.rm = TRUE), 
            `0.99`=quantile(GDP_PC_CHANGE, probs = 0.99, na.rm = TRUE))



global_dat<- global_dat %>% group_by(ECONOMY) %>% 
  mutate(GDP_PC_CHANGE=case_when(GDP_PC_CHANGE<quantile(GDP_PC_CHANGE, probs=0.01, na.rm=T)~NA_real_, 
                              GDP_PC_CHANGE>quantile(GDP_PC_CHANGE, probs=0.99, na.rm=T)~NA_real_,
                              TRUE~GDP_PC_CHANGE)) %>% ungroup()
           



global_dat %>% group_by(ECONOMY) %>% 
  summarise(n(),  n.notmiss=sum(!is.na(GDP_PC_CHANGE)),
            min=min(GDP_PC_CHANGE, na.rm = TRUE), 
            max=max(GDP_PC_CHANGE,  na.rm = TRUE))


quantile(global_dat$GDP_PC_CHANGE, seq(0,1,0.01), na.rm = TRUE)


table(is.na(global_dat$GDP_PC_CHANGE))

```

### POVERTY

100 represents the highest level of deprivation and a value of 0 the lowest

```{r}

global_dat<- global_dat %>% mutate(GDP_log=ifelse(GDP_17_19<1000, NA, log(GDP_17_19)))

global_dat<- global_dat %>% mutate(ECON_URBAN=paste(ECONOMY, urban, sep=", "))

# Split dataset by ECONOMY class
economy_groups <- split(global_dat, global_dat$ECON_URBAN)

# Create an empty list to store `lme` results by variable
lme_results_list <- list()

# Loop through each ECONOMY class
for (economy in names(economy_groups)) {
  
  # Subset data
  data_subset <- economy_groups[[economy]]
  
  # Fit `lme` model separately for each ECONOMY class
  mod <- lme(fixed = log(poverty_20) ~ GDP_log, 
             random = ~ 1 | ISO_A3,  # Random intercept for country
             data = data_subset, method = "REML", na.action = na.exclude,
             control = lmeControl(opt = "optim"))
  
  # Extract model summary
  model_summary <- as.data.frame(summary(mod)$tTable)  # Extract fixed effects
  model_summary$term <- rownames(model_summary)  # Store term names
  colnames(model_summary) <- c("estimate", "std.error", "DF", "t.value", "p.value", "term")
  
  # Compute 95% Confidence Intervals
  model_summary <- model_summary %>%
          filter(term == "GDP_log") %>%
    mutate(lower = estimate - 1.96 * std.error,
           upper = estimate + 1.96 * std.error,
           ECON_URBAN = economy) %>%
    select(ECON_URBAN, term, estimate, std.error, p.value, lower, upper)
  
  # Store the results for this ECONOMY class
  lme_results_list[[economy]] <- model_summary
}

# Combine all results into a single dataframe
lme_results_df <- bind_rows(lme_results_list)

# Round numeric values to 4 decimals
lme_results_df <- lme_results_df %>%
  mutate_if(is.numeric, round, 4)

# View the final combined dataframe
print(lme_results_df)

# Display first element of results list
lme_results_list[[1]]

lme_results_df<- lme_results_df %>% select(ECON_URBAN, estimate) %>% rename(poverty_coef=estimate)


global_dat<- global_dat %>% left_join(lme_results_df, by="ECON_URBAN")



global_dat <- global_dat %>%
  mutate(
    GDP_diff = log(GDP_00_02) - log(GDP_17_19),  # Compute GDP log difference
    log_poverty_2000 = log(poverty_20) + (poverty_coef * GDP_diff),  # Apply the coefficient
    poverty_00 = exp(log_poverty_2000)  # Convert back from log scale
  )

global_dat<- global_dat %>% 
  mutate(poverty_00=ifelse(is.infinite(poverty_00), NA, poverty_00))

quantile(global_dat$poverty_00, seq(0,1, 0.01), na.rm=T)

quantile(global_dat$poverty_20, seq(0,1, 0.01), na.rm=T)


cor(global_dat$poverty_00, global_dat$poverty_20, use = "complete.obs")

```



```{r}

global_dat<- global_dat %>% 
  mutate(POVERTY_CHANGE=round((poverty_20-poverty_00)/poverty_00, 4))

look<-global_dat %>% select(poverty_20, poverty_00, poverty_coef, GDP_diff,GDP_00_02, GDP_17_19, GDP_CHANGE, POVERTY_CHANGE)


##trim 0.01 and 0.99 percentiles by Economy
#looks good, dont trim
trim_cats<- global_dat %>% group_by(ECONOMY) %>% 
  summarise(n(), n.notmiss=sum(!is.na(POVERTY_CHANGE)),
            `0.01`=quantile(POVERTY_CHANGE, probs = 0.01, na.rm = TRUE), 
            `0.99`=quantile(POVERTY_CHANGE, probs = 0.99, na.rm = TRUE))



#global_dat<- global_dat %>% group_by(ECONOMY) %>% 
#  mutate(POVERTY_CHANGE=case_when(POVERTY_CHANGE<quantile(POVERTY_CHANGE, probs=0.01, na.rm=T)~NA_real_, 
#                              POVERTY_CHANGE>quantile(POVERTY_CHANGE, probs=0.99, na.rm=T)~NA_real_,
#                              TRUE~POVERTY_CHANGE)) %>% ungroup()
           



global_dat %>% group_by(ECONOMY) %>% 
  summarise(n(),  n.notmiss=sum(!is.na(POVERTY_CHANGE)),
            min=min(POVERTY_CHANGE, na.rm = TRUE), 
            max=max(POVERTY_CHANGE,  na.rm = TRUE))


quantile(global_dat$POVERTY_CHANGE, seq(0,1,0.01), na.rm = TRUE)


table(is.na(global_dat$POVERTY_CHANGE))

global_dat %>% group_by(ECON_URBAN) %>% 
  summarise(cor(POP_CHANGE, POVERTY_CHANGE, use="complete.obs"))


```



### Age  

create working age groups 

https://www.oecd.org/en/data/indicators/employment-rate-by-age-group.html 

people aged 15-64 (the working age population)

15 to 24 (those just entering the labour market following education); people aged 25 to 54 (those in their prime working lives); people aged 55 to 64 (those passing the peak of their career and approaching retirement)


```{r}

#working age categories
# work 15-64
#young 15-24
#prime 25-54
#old 55-64

colnames(global_dat)

pct_00_work <- paste0("pct_age_", c(seq(15, 60, by=5)), "_2000")
pct_20_work <- paste0("pct_age_", c(seq(15, 60, by=5)), "_2020")

pct_00_work_young <- paste0("pct_age_", c(seq(15, 20, by=5)), "_2000")
pct_20_work_young <- paste0("pct_age_", c(seq(15, 20, by=5)), "_2020")

pct_00_work_prime <- paste0("pct_age_", c(seq(25, 50, by=5)), "_2000")
pct_20_work_prime <- paste0("pct_age_", c(seq(25, 50, by=5)), "_2020")

pct_00_work_old <- paste0("pct_age_", c(seq(55, 60, by=5)), "_2000")
pct_20_work_old <- paste0("pct_age_", c(seq(55, 60, by=5)), "_2020")

pct_00_retire <- paste0("pct_age_", c(seq(65, 80, by=5)), "_2000")
pct_20_retire <- paste0("pct_age_", c(seq(65, 80, by=5)), "_2020")


global_dat <- global_dat %>%
  mutate(pct_age_work_2000 = rowSums(across(all_of(pct_00_work)))) %>% 
  mutate(pct_age_work_2020 = rowSums(across(all_of(pct_20_work)))) %>% 
  #young wrk
  mutate(pct_age_work_young_2000 = rowSums(across(all_of(pct_00_work_young)))) %>% 
  mutate(pct_age_work_young_2020 = rowSums(across(all_of(pct_20_work_young)))) %>% 
  #prime wrk
  mutate(pct_age_work_prime_2000 = rowSums(across(all_of(pct_00_work_prime)))) %>% 
  mutate(pct_age_work_prime_2020 = rowSums(across(all_of(pct_20_work_prime)))) %>% 
  #old wrk
  mutate(pct_age_work_old_2000 = rowSums(across(all_of(pct_00_work_old)))) %>% 
  mutate(pct_age_work_old_2020 = rowSums(across(all_of(pct_20_work_old)))) %>% 
  #retire
  mutate(pct_age_retire_2000 = rowSums(across(all_of(pct_00_retire)))) %>% 
  mutate(pct_age_retire_2020 = rowSums(across(all_of(pct_20_retire))))  



check<- global_dat %>% select(total_age_00,pct_00_work, pct_age_work_2000)


```


```{r}

#now pair up at take differences 

col_diff<-  c(paste0("pct_age_", c(0, 1, seq(5, 80, by=5))), 
              "pct_age_work", "pct_age_work_young", 
              "pct_age_work_prime", "pct_age_work_old", "pct_age_retire")


for (col in col_diff) {
  global_dat <- global_dat %>%
    mutate("{col}_DIFF" := !!sym(paste0(col, "_2020")) - !!sym(paste0(col, "_2000")))
}


summary(global_dat %>% select(pct_age_0_DIFF:pct_age_retire_DIFF))


#trim


age_diff_names<- paste0(col_diff, "_DIFF")

global_dat <- global_dat %>%
  group_by(ECONOMY) %>%
  mutate(across(all_of(age_diff_names), 
                ~ case_when(
                  . < quantile(., probs = 0.01, na.rm = TRUE) ~ NA_real_,
                  . > quantile(., probs = 0.99, na.rm = TRUE) ~ NA_real_,
                  TRUE ~ .
                ))) %>%
  ungroup()


global_dat <- global_dat %>%
  group_by(ECONOMY) %>%
  mutate(across(all_of(age_diff_names), 
                ~ case_when(
                  is.na(POP_CHANGE) ~ NA_real_,
                  TRUE ~ .
                ))) %>%
  ungroup()


summary(global_dat %>%   select(pct_age_0_DIFF:pct_age_retire_DIFF))


```



```{r}

#median age

global_dat<- global_dat %>% 
  mutate(median_age_DIFF=median_age_2020-median_age_2000, 
         median_age_CHANGE=(median_age_2020-median_age_2000)/median_age_2000)

summary(global_dat$median_age_DIFF)
summary(global_dat$median_age_CHANGE)


```




```{r}

#sex

global_dat<- global_dat %>% mutate(pct_females_DIFF=pct_females_20-pct_females_00, 
                      pct_males_DIFF=pct_males_20-pct_males_00 )

summary(global_dat$pct_males_DIFF)
summary(global_dat$pct_females_DIFF)


```



### EXPORT


```{r}


global_dat<- global_dat %>% select(ISO_A3:urban, urban_rural, POP_CHANGE, GDP_CHANGE, GDP_PC_CHANGE,
                                   HDI_CHANGE, HDI_CHANGE_INT_00, HDI_DIFF_INT_00,POVERTY_CHANGE,
                      pct_age_0_DIFF:pct_age_retire_DIFF, median_age_DIFF, median_age_CHANGE,
                      pct_males_DIFF, pct_females_DIFF,
                      everything())


relationships<-cor(global_dat %>% select(POP_CHANGE:pct_females_DIFF), use = "complete.obs")


```


```{r}

saveRDS(global_dat, file = "/mnt/theia/implications/dmed_global_data/Global Implications Datasets/global_dat_ready.rds")


write_csv(global_dat, file = "/mnt/theia/implications/dmed_global_data/Global Implications Datasets/global_dat_ready.csv")



```



